Categorical Predictor Embeddings in Actuarial Modeling

### 2021-02-03 manuscript/manuscript.Rmd
edits

Extracting and interpreting trained embeddings, including visualization techniques Can we explain the learned 
embeddings using a GLM? distance to water etc Rainfall Density Distance to coast

@@

How can embedding layers be used in GLM models? (Potential uses of embedding layers as a feature engineering technique 
for GLM) Transfer learned embeddings to GLM - backprop on NN and use as preprocessing Train GLM on embedding layers - 
backprop on 1 layer NN

>>>>

- model explainability is important in insurance
- the more we can learn about how we arrive at our models the better
- cite some existing work on explainable models in actuarial literature to show people care
- refer back to some definitions from previous sections
- show some embedding weights from our models - 1d line plot
- (need a multidimensional embedding for this) do some pca/tsne
- stress that relationship of embedding weights to response variable may be nonlinear depending on architecture

@@

- get weights from NN and use in place of categorical variables in GLM?
- train GLM using backprop w/ embedding layer (OK maybe this ought to be absorbed in the modeling section and we add this as a separate model?)
